\tb{Place of Residence and Political Attitudes in Democracies Worldwide \\ {\large Point-Based Outline} }

### 2018-11-07 Outline/OutlineJLin.tex
updated outline

\begin{enumerate}
\item Introduction to the Paper: The Intersection between Place of Residence and Political Attitudes\footnote{The materials used in this research project can all be found in this Git Repository \url{https://github.com/lin-jennifer/CompRuralPolitics.git} Which also includes the backstage files used to generate this document along with the Annotated Bibliography and detailed breakdown of analysis results}
\begin{enumerate}
	\item The Big Picture: The United States and the 2016 Election: Rural voters have helped the Republican secure their victory and these voters are core to Trump's base \citep{walsh_putting_2012}. Can we observe these effects elsewhere?
	\item Guiding Question: Does place of residence influence political attitudes and ideology? How do certain factors of the regime, including its age and electoral formula, influence these results?
	\item Brief summary of key conclusions from Literature Review and Data Analysis
\end{enumerate}
\item Literature Review
\begin{enumerate}
	\item Analysis of the Rural Consciousness in the United States
	\item Analysis of the Rural Consciousness in other countries in brief
	\item Discern what the literature has to say about the ties between Rurality and political attitudes - As of now, it says that people who live in rural areas tend to be more religious and more conservative on social issues. However, they can also be liberal when it comes to the economy since that is where their own economic interests lie.
\end{enumerate}
\item Research Design: Methods and Variables 
\begin{enumerate}
	\item Data: CSES Module 4 \url{http://www.cses.org/datacenter/module4/module4.htm}
	\item Cases: The cases that are considered in this study are based on those available in the CSES dataset.\footnote{The CSES provides a brief synopsis of the elections that were used for the data collection here" \url{http://www.cses.org/datacenter/module4/data/cses4_codebook_part5_election_summaries.txt}.}
	\item Methodology: See Section 2 for detailed breakdown
\end{enumerate}
\item Results: Broken down by Regression Model
\begin{enumerate}
	\item Regression: Across all polities: Place on ideology on ideology
	\item Regression: Interaction of place of residence and level of democracy on ideology
	\item Regression: Interaction of place of residence and regime electoral formula on ideology
	\item Regression: Interaction of place of residence and age of regime on ideology
	\item Regression: Consideration of place of residence, level of democracy, regime electoral formula, and age of regime on political ideology
\end{enumerate}
\item Conclusion: Place of residence matters.
\begin{enumerate}
	\item When regressed on itself with regime variables, rural residents are significantly more conservative than urban residents
	\item Directions for future research
	\begin{enumerate}
		\item Consdier any other possible variables that influence the interaction since research in American politics concludes that there are other favtors such as education and income that matter in the relationship observed \citep{gimpel_rural_2006}
	\end{enumerate}
\end{enumerate}
\end{enumerate}

>>>>

\begin{enumerate}
\item Introduction to the Paper: The Intersection between Place of Residence and Political Attitudes\footnote{The materials used in this research project can all be found in this Git Repository \url{https://github.com/lin-jennifer/CompRuralPolitics.git} Which also includes the backstage files used to generate this document along with the Annotated Bibliography and detailed breakdown of analysis results}
\begin{enumerate}
	\item The Big Picture: The United States and the 2016 Election: Rural voters have helped the Republican secure their victory and these voters are core to Trump's base \citep{walsh_putting_2012}. Can we observe these effects elsewhere?
	\item Guiding Question: Does place of residence influence political attitudes and ideology? How do certain factors of the regime, including its age and electoral formula, influence these results?
	\item Brief summary of key conclusions from Literature Review and Data Analysis
\end{enumerate}
\item Literature Review
\begin{enumerate}
	\item Analysis of the Rural Consciousness in the United States and around the world with considerations of the country's political culture.
	\item Discern what the literature has to say about the ties between rurality and political attitudes - As of now, it says that people who live in rural areas tend to be more religious and more conservative on social issues. However, they can also be liberal when it comes to the economy since that is where their own economic interests lie.
	\item Overview of the elections that are considered in the CSES, including countries reported, actors involved and other key characteristics of the election. 
\end{enumerate}
\item Research Design: Methods and Variables 
\begin{enumerate}
	\item Data: CSES Module 4 \url{http://www.cses.org/datacenter/module4/module4.htm}
	\item Cases: The cases that are considered in this study are based on those available in the CSES dataset.\footnote{The CSES provides a brief synopsis of the elections that were used for the data collection here" \url{http://www.cses.org/datacenter/module4/data/cses4_codebook_part5_election_summaries.txt}.}
	\item Methodology: See Section 2 for detailed breakdown
\end{enumerate}
\item Results: Broken down by Regression Model
\begin{enumerate}
	\item Regression: Across all polities: Place on ideology on ideology
	\item Regression: Interaction of place of residence and level of democracy on ideology
	\item Regression: Interaction of place of residence and regime electoral formula on ideology
	\item Regression: Interaction of place of residence and age of regime on ideology
	\item Regression: Consideration of place of residence, level of democracy, regime electoral formula, and age of regime on political ideology
\end{enumerate}
\item Conclusion: Place of residence matters, but there is still a lot of noise in the model.
\begin{enumerate}
	\item When regressed on itself with regime variables, rural residents are significantly more conservative than urban residents
	\item Directions for future research
	\begin{enumerate}
		\item Consider any other possible variables that influence the interaction since research in American politics concludes that there are other factors such as education and income that matter in the relationship observed \citep{gimpel_rural_2006}
	\end{enumerate}
\end{enumerate}
\end{enumerate}
